Longer Term All-Cause and Cardiovascular Mortality With Intensive Blood Pressure Control

### 2024-07-18 index.qmd
DR's feedback
dropping some of the more tedious things from my slides so that this 12
minute presentation doesn't try to do too much.

---
title: "Longer Term All-Cause and Cardiovascular Mortality With Intensive Blood Pressure Control"
subtitle: "A Secondary Analysis of a Randomized Clinical Trial"
author: "Byron C. Jaeger, PhD"
institute: "Wake Forest University School of Medicine"
format: 
  revealjs:
    slide-number: true
    footer: Slides available at
    width: 1280
    height: 720
    fig-dpi: 300
    fig-width: 8
    fig-height: 6
    fig-align: "center"
    message: false
    bibliography: doc/refs.bib
    reference-location: document
knitr:
  opts_chunk:
    out.width: "100%"
---

@@

@@

- How did we analyze the longer term follow-up?

@@

## What's changed?

@@

bp_viz$levels + 
  theme_fig(legend.position = 'top')

@@

bp_viz$diff + 
  theme_fig(legend.position = 'top') + 
  ylab("Between-group difference in SBP, mm Hg")

@@

::: {.column width="15%"}
This update is a bit of a head-scratcher.
:::

@@

>>>>

---
title: "Longer Term All-Cause and Cardiovascular Mortality With Intensive Blood Pressure Control"
subtitle: "A Secondary Analysis of a Randomized Clinical Trial"
author: "Byron C. Jaeger, PhD"
institute: "Wake Forest University School of Medicine"
format: 
  revealjs:
    slide-number: true
    footer: Slides available at https://www.byronjaeger.com/talk/ (google byron jaeger biostats talks)
    width: 1280
    height: 720
    fig-dpi: 300
    fig-width: 8
    fig-height: 6
    fig-align: "center"
    message: false
    bibliography: doc/refs.bib
    reference-location: document
knitr:
  opts_chunk:
    out.width: "100%"
---

@@

## Disclosures

I have nothing to disclose.

## TL;DR

- After SPRINT, from 2016-2020, the mean systolic blood pressure levels of participants returned to about 140 mm Hg, and the benefit of intensive blood pressure control attenuated.

- Additional follow-up from 2020-2023 provides an opportunity to think carefully about interventions that had a beneficial effect.

@@

@@

## Number of events

@@

bp_viz$levels_ehr_only + 
  theme_fig(legend.position = 'top')

@@

bp_viz$diff_ehr_only + 
  theme_fig(legend.position = 'top') + 
  ylab("Between-group difference in SBP, mm Hg")

@@

::: {.column width="15%"}
A bit of a head-scratcher.
:::

@@

## Conclusion

- After SPRINT, from 2016-2020, SBP returned to about 140 mm Hg, and the benefit of intensive blood pressure control attenuated.

- The latest update shows what appears to be a resurfaced benefit in terms of CVD mortality. This could be attributed to:

    + participants in the intensive blood pressure control group who maintained control after the trial

    + intensive blood pressure control has higher estimated benefit for younger adults.

::: {style="font-size: 2em"}
# BONUS ROUND
:::
